---
title: "Fullmixedeffectsmodel"
author: "BrinnaeBent"
date: "September 16, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#This file looks models the interactions between skin tone, device, device type, and activity condition. 

#Input: File from Import_Raw_Data_Merge.csv
#Output: Mixed Effects Models and Interaction Model for STEP Analysis

```{r}
df <- read.csv("filepath\\STEP_A2.csv", header=FALSE, stringsAsFactors = FALSE)
colnames(df) <- c("ID", "Timestamp", "ECGHR", "WSHR", "Diff", "Device", "Type", "Condition", "FST")

```
#Mixed Model all variables

```{r}

# Model for All variables 
library(lme4)

model = lmer(Diff ~ FST + Device + Condition + Type + (1|ID), data=df, REML=FALSE)
model.null = lmer(Diff ~ 1 + (1|ID), data=df, REML=FALSE)

summary(model)
#summary(model.null)
anovatotal = anova(model.null, model)
print(anovatotal)

library(lmerTest)

#lrtest(model, model.null)


```

#Mixed Model Skin Tone only

```{r}

# Model for FST 
library(lme4)

modelFST = lmer(Diff ~ FST + (1|ID), data=df, REML=FALSE)
model.nullFST = lmer(Diff ~ 1 + (1|ID), data=df, REML=FALSE)

summary(modelFST)
summary(model.nullFST)
anovaFST = anova(model.nullFST, modelFST)
print(anovaFST)

```

# Mixed Model Activity Condition Only

```{r}

# Model for Condition (Walking, Rest, Typing, Deep Breathing)
library(lme4)

modelC = lmer(Diff ~ Condition + (1|ID), data=df, REML=FALSE)
model.nullC = lmer(Diff ~ 1 + (1|ID), data=df, REML=FALSE)

summary(modelC)
summary(model.nullC)
anovaC = anova(model.nullC, modelC)
print(anovaC)
```

#Mixed Model for Device

```{r}

# Model for Device (Apple Watch, Fitbit, Garmin, Biovotion, Empatica, Xiaomi Miband)
library(lme4)

modelD = lmer(Diff ~ Device + (1|ID), data=df, REML=FALSE)
model.nullD = lmer(Diff ~ 1 + (1|ID), data=df, REML=FALSE)

summary(modelD)
summary(model.nullD)
anovaD = anova(model.nullD, modelD)
print(anovaD)
```

#Mixed Model for Consumer vs. Research Type

```{r}

# Model for Type (Consumer or Research)
library(lme4)

modelT = lmer(Diff ~ Type + (1|ID), data=df, REML=FALSE)
model.nullT = lmer(Diff ~ 1 + (1|ID), data=df, REML=FALSE)

summary(modelT)
summary(model.nullT)
anovaT = anova(model.nullD, modelT)
print(anovaT)
```

# Compare ANOVA for individual models and full model

```{r}
print('Anova Total Model p-value = ') 
print(anovatotal$`Pr(>Chisq)`[2])

print('Anova Skin Tone Model p-value = ')
print(anovaFST$`Pr(>Chisq)`[2])

print('Anova Condition (Walk, Rest, Type, Deep Breathe) Model p-value = ')
print(anovaC$`Pr(>Chisq)`[2])

print('Anova Device (Apple Watch, Fitbit, Miband, Garmin, Biovotion, Empatica) Model p-value = ')
print(anovaD$`Pr(>Chisq)`[2])

print('Anova Type of Device (Consumer, Research) Model p-value = ')
print(anovaT$`Pr(>Chisq)`[2])
```

# Interaction Model between Skin Tone and Device

```{r}

library(lme4)
library(lmtest)

modelI = lmer(Diff ~ FST*Device + (1|ID), data=df, REML=FALSE)
modelI2 = lmer(Diff ~ FST + Device + (1|ID), data=df, REML=FALSE)

lrtest(modelI, modelI2)

#model.nullI = lmer(Diff ~ 1 + (1|ID), data=df, REML=FALSE)
summary(modelI)
#summary(model.nullI)
#anovaI = anova(model.nullI, modelI)
#print(anovaI)
```
